---
title: "A closer look at the Religions of Holocaust victims"
subtitle: "An analysis of the religions of the victims at Auschwitz from 1941 to 1943"
author: 
  - Aryaman Suri
thanks: "Code and data are available at: https://github.com/aryamansuri/Holocaust-Victims"
date: today
date-format: long
format: pdf
number-sections: true
toc: true
toc-depth: 2
bibliography: references.bib
warning : false
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
library(here)
library(knitr)
library(tinytex)
library(janitor)
library(ggplot2)
```

```{r}
#| echo: false
#| include: true
#| message: false

## Read the data
raw_data <-
  read_csv(here("Data/raw_data/raw_data.csv"))
  show_col_types = FALSE
  
cleaned_data <-
  read_csv(here("Data/analysis_data/cleaned_data.csv"))
  show_col_types = FALSE
```

# **Introduction**:

The Holocaust stands as one of the darkest chapters in human history, marked by the systematic persecution and extermination of millions of innocent lives. Among the most infamous sites of this tragedy is Auschwitz, a concentration and extermination camp where over one million people, predominantly Jews, were murdered by the Nazis during World War II. In an effort to shed light on this harrowing history, this project endeavors to explore religions of those victims.
We use R (@citeR) for this analysis, along with shiny (@shiny), knitr (@citeknitr), tidyverse (@citetidyverse), dplyr (@citedplyr), janitor (@citejanitor) and here (@citehere) packages. The use of these is mentioned later in our paper.

# **Data:**

Just as data sets have played a crucial role in understanding the trans-Atlantic slave trade (@reference1), they are equally essential in comprehending the magnitude of the Holocaust. By meticulously collecting and analyzing data related to Auschwitz victims, I aim to uncover insights into the demographics of those who suffered and perished in the camp.

## Raw Data

We get the raw data from the United States Holocaust Memorial Museum website (@reference2). This data includes the first names, last names, dates of birth and death and religion of the victims in Auschwitz from 1941 to 1943. We store this data in a raw data csv. We can see a portion of the raw data we were working with in Table 1 (see @tbl-raw_data).

```{r}
#| echo: false
#| message: false
#| label: tbl-raw_data
#| tbl-cap: "A look at a portion of the raw data"
#| warning: false

head(raw_data, 5)
```

## Cleaning Data

Since we are only interested in the religions of the victims for this project, we cleaned the data using count() (@R-count) and obtained a table with two columns. The first column is the religion of the victims, and the second column contains the count of the respective religion, in terms of victims. We can see the data that we cleaned and working with in Table 2(see @tbl-clean_data).

```{r}
#| echo: false
#| message: false
#| label: tbl-clean_data
#| tbl-cap: "A look at the clean data"
#| warning: false

view(cleaned_data)
```


# **Graph and create shiny**

We now graph our cleaned data, keeping the religions of the victims as our x axis and the death toll as our y axis. We use ggplot (@ggplot2) to make this graph. We then use our custom colours list to fill in our bars and add labels to the graph. We can see the final graph in @fig-graph1.

```{r}
#| echo: false
#| eval: true
#| message: false
#| include: true
#| label: graph1
#| fig.cap: "Graph showing the religions of the victims"
#| warning: false


# Define custom color palette
custom_colors <- c("#E41A1C", "#377EB8", "#4DAF4A", "#FF7F00", "#984EA3", "#FFD700", "#F781BF", "#A65628", "#FF5733", "#6A5ACD", "#6495ED", "#00CED1", "#2E8B57", "#FF8C00", "#B22222", "#800000", "#8B4513", "#8A2BE2", "#20B2AA")

# Plotting the graph with custom colors, count labels, and x-axis label
ggplot(cleaned_data, aes(x = Religion, y = n, fill = Religion)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = -0.5, color = "black", size = 3) +  # Add count labels above each bar
  scale_fill_manual(values = custom_colors) +  # Apply custom colors
  labs(title = "Auschwitz Victims by Religion",
       x = NULL,  # Remove x-axis label
       y = "Number of Victims") +
  xlab("Religions of the victims") +  # Add x-axis label
  theme_minimal() +
  theme(legend.title = element_blank(),  # Remove legend title
        axis.text.x = element_blank(),  # Remove x-axis labels
        axis.ticks.x = element_blank()) +  # Remove x-axis ticks
  theme(legend.position = "bottom")
```


After our graph is made, we used Shiny (@shiny) to create an interactive graph and an interactive table. These show the number of people murdered by religion and allows the user to specify the groups they are interested in seeing data for. This app is published using posit cloud and can be found at https://posit.cloud/content/7881580. 


# **Conclusion:**

In conclusion, our exploration of the religious affiliations of Auschwitz victims sheds light on the diverse identities and backgrounds of those who perished in one of humanity's darkest chapters. Through meticulous data analysis, we've underscored the importance of recognizing and commemorating the individual lives lost in the Holocaust. As we honor the memory of these victims, we reaffirm our commitment to preserving their stories for future generations. By continuing to delve into the complexities of this history, we strive to foster empathy, understanding, and a solemn acknowledgment of the enduring impact of genocide. May their legacy serve as a poignant reminder of the ongoing imperative to uphold human dignity and prevent such atrocities from ever occurring again.

# **References:**
